---
title: "population"
author: "Brahmantio, B. B. & van Doorn, J."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{population}
  %\VignetteEngine{rmarkdown::render}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(jsonlite)
library(shiny)
library(lab5group8)
```

# Using the population package
## Introduction
This package is an excercise in building a package, working with web-API's, and creating an app using Shiny. Specifically, this package contains two functions `r population$new()` and `r shinyApp(ui = ui, server = server)`.

## population
You can create an object of the class *population* with the following command:

```{r}
popul <- population$new()
```
It has two methods:
`r popul$municipalities` returns a list of all municipalities in the dataset.
`r popul$population_data("Stockholm")` returns a dataframe with the year and the population size in that year for a specified municipality. In this case Stockholm.

